Predicting the Likelihood of Climate-Friendly Actions: Insights from Age and Educational Attainment

### 2024-12-11 paper/climate_change.qmd
save models into correct model folder

knitr::include_graphics(here::here("data/04-model_data/vehicle_electric_tree.png"))

@@

knitr::include_graphics(here::here("data/04-model_data/home_improvement_tree.png"))

@@

knitr::include_graphics(here::here("data/04-model_data/protein_alternative_tree.png"))

@@

This outcome suggests that either the input data lacks variability in relevant features, or the behavior of minimizing car use is widespread and consistent across the sample population. Consequently, the model does not differentiate between subgroups and treats all individuals as having the same likelihood of engaging in this behavior.
```{r}
#| warning: false
#| echo: false
#| message: false
#| label: @fig-thirteen
#| fig-cap: Probability tree for likelihood of minimizing car use, predicted by age and education.

knitr::include_graphics(here::here("data/04-model_data/minimize_car_tree.png"))

@@

knitr::include_graphics(here::here("data/04-model_data/green_product_tree.png"))

@@

knitr::include_graphics(here::here("data/04-model_data/reduce_hydro_tree.png"))

@@

knitr::include_graphics(here::here("data/04-model_data/reduce_waste_tree.png"))

@@

knitr::include_graphics(here::here("data/04-model_data/sort_waste_tree.png"))

@@

knitr::include_graphics(here::here("data/04-model_data/short_distance_tree.png"))

@@

# Load the model accuracy data from the saved CSV
model_accuracies <- read.csv(here::here("data/04-model_data/model_accuracies.csv"))

>>>>

knitr::include_graphics(here::here("models/vehicle_electric_tree.png"))

@@

knitr::include_graphics(here::here("models/home_improvement_tree.png"))

@@

knitr::include_graphics(here::here("models/protein_alternative_tree.png"))

@@

This outcome suggests that either the input data lacks variability in relevant features, or the behavior of minimizing car use is widespread and consistent across the sample population. Consequently, the model does not differentiate between subgroups and treats all individuals as having the same likelihood of engaging in this behavior.
```{r}
#| warning: false
#| echo: false
#| message: false
#| label: fig-thirteen
#| fig-cap: Probability tree for likelihood of minimizing car use, predicted by age and education.

knitr::include_graphics(here::here("models/minimize_car_tree.png"))

@@

knitr::include_graphics(here::here("models/green_product_tree.png"))

@@

knitr::include_graphics(here::here("models/reduce_hydro_tree.png"))

@@

knitr::include_graphics(here::here("models/reduce_waste_tree.png"))

@@

knitr::include_graphics(here::here("models/sort_waste_tree.png"))

@@

knitr::include_graphics(here::here("models/short_distance_tree.png"))

@@

# Load the model accuracy data from the saved CSV
model_accuracies <- read.csv(here::here("models/model_accuracies.csv"))
